Interleaved Serial and Decision-Theoretic Planning for High-Level Robot Control

### 2011-01-28 subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
AAAI version of the switching planner paper

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Switching in Continual Planning for Practical Robot Control}
\title{A Switching Planner for Combined Task and Observation Planning}
%\title{A Continual Planner that Switches Between Sequential and
%  Decision-Theoretic Planning} 
\author{Submission 86}
\setcounter{secnumdepth}{0}

@@

Realistic robot planning problems in uncertain environments often
require achieving tasks while also finding out about the
world. Because the world state cannot be observed directly, these
problems are naturally represented as partially observable Markov
decision problems (POMDPs). However, these are typically intractable
for realistic problems.
%%
We present a \emph{switching planner} that employs fast sequential
planning to decide on the overall strategy, and uses a
decision-theoretic planner to solve the subproblems where partial
observability will significantly impact the quality of the plan. We
demonstrate the approach in a realistic robot exploration domain.

>>>>

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

%% \title{Interleaved Serial and Decision-Theoretic Planning for
%% Practical Robot Control}

\title{Interleaved Serial and Decision-Theoretic Planning for High-Level Robot Control}

%% \title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}
\setcounter{secnumdepth}{0}

@@

%% Those processes must

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit useful
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We demonstrate our approach
in large problems from a realistic robot exploration domain.

%% partial observability

%% In cooperation with execution monitoring, it must perform repair
%% and/or replanning in order to seamlessly accommodate exogenous events,
%% changing objectives, and the underlying unpredictability of the
%% environment.

%% Realistic robot planning problems in uncertain environments often
%% require achieving tasks while also finding out about the
%% world. Because the world state cannot be observed directly, these
%% problems are naturally represented as partially observable Markov
%% decision problems (POMDPs). However, these are typically intractable
%% for realistic problems.
%%
